---
title: "Entry and Exit of formal firms in Vietnam 2000-2015"
thanks: "I would like to thank Sam Kortum and Costas Arkolakis for comments on this note"
author: 
    - Nghiem Q. Huynh^[Yale University, nghiem.huynh@yale.edu]
output: 
  bookdown::pdf_document2: 
    toc: false
    keep_tex: true
  bookdown::word_document2: default  
abstract: "Using annual firm survey, I follow @Dunne1988 to compute summary statistics of formal firms in Vietnam from 2000 to 2015. "
keywords: " "
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: margin=1in
fontfamily: charter
fontsize: 12pt
bibliography: "entry_exit.bib"
link-citations: true
---

```{r setup, include=FALSE}
# Chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  #warning=FALSE, 
  #message=FALSE,
  #fig.width = 6,
  fig.asp = 0.8,
  out.width = "90%"
)
```

```{r load-files, include= FALSE}
library(here)

source(file = here("inst", "rmd", "required_packages.R"))
```

```{r bibtex, include=FALSE, eval=FALSE}
file.copy(from = "/Volumes/GoogleDrive/My Drive/MendeleyBibTeX/entry_exit.bib", 
          to = here("inst", "rmd"), 
          overwrite = T)
```

```{r theme-ggplot2, echo = FALSE}
library(ggplot2)

theme_nghiem <- function(base_size = 14) {
  theme_classic(base_size = base_size) %+replace%
    theme(
      # L'ensemble de la figure
      plot.title = element_text(size = rel(1), face = "bold", margin = margin(0,0,5,0), hjust = 0),
      # Zone où se situe le graphique
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      # Les axes
      axis.title = element_text(size = rel(0.85)),
      axis.text = element_text(size = rel(0.70)),
      #axis.line = element_line(color = "black", arrow = arrow(length = unit(0.3, "lines"), type = "closed"))
      # La légende
      legend.title = element_text(size = rel(0.85), face = "bold"),
      legend.text = element_text(size = rel(0.70)),
      legend.key = element_rect(fill = "transparent", colour = NA),
      legend.key.size = unit(1.5, "lines"),
      legend.background = element_rect(fill = "transparent", colour = NA),
      legend.position = "bottom"
    )
}
# Changing the default theme
theme_set(theme_nghiem())
```

# Single plant share

```{r single-plant-g, fig.align='center', fig.cap= 'Single plant share'}
knitr::include_graphics(path = here("inst", "tmp", "figure",
                                    "single_plant_share.png"))
```

# Entry and exit of all firms

```{r entry-exit-dta, include= F}
entry_exit_dta <- fread(here("inst", "tmp", "entry_exit_dta.csv"))

t_dta <- dcast(melt(entry_exit_dta, id.vars = "svyear"), 
     variable ~ svyear, 
     value.var = "value")
# 
# t_dta <- t_dta %>% mutate_if(is.numeric, ~round(., 3)) 

t_dta[t_dta$variable %like% "E", type := "entry"]
t_dta[t_dta$variable %like% "X", type := "exit"]

t_dta <- t_dta[order(type), !c("type")]

t_dta$variable <- c("Entry Rate (ER)", 
                    "Entrant Market Share (ESH)",
                    "Entrant Relative Size (ERS)",
                    "Exit Rate (XR)",
                    "Exiter Market Share (XRH)",
                    "Exiter Relative Size (XRS)")

colnames(t_dta)[1] <- ""
```

```{r entry-exit-tab}
kbl(t_dta, 
    digits = 3, 
             format = "latex",
             booktabs = TRUE, 
             caption = "Entry and Exit all firms", 
             table.envir = "table", 
             position = "!h") %>% 
      #kable_classic(full_width = T) %>% 
      pack_rows(index = c("Entry" = 3, "Exit" = 3))


```

```{r entry-exit-g, fig.align='center', fig.cap= 'Entry-Exit'}
knitr::include_graphics(path = here("inst", "tmp", "figure",
                                    "entry_exit_g.png"))
```

## Discussion

1.  Entry rate is about 4 times that of the US.
2.  The other rates are comparable

Why entry rate is so high?

1.  The annualized rate seems comparable to @McCaig2021 who reports the entry rate of firms 2000-2017 at 27% annually. Thus, the data seem trustworthy.
2.  The rate is high even compared to developing countries as documented in @McCaig2021 and much higher than developed countries. @McCaig2021 observe that this number is comparable to other countries that transition out of centrally planned economies.

# Manufacturing
