---
title: "Entry and Exit of formal firms in Vietnam 2000-2015"
thanks: "I would like to thank Sam Kortum and Costas Arkolakis for comments on this note"
author: 
    - Nghiem Q. Huynh^[Yale University, nghiem.huynh@yale.edu]
output: 
  bookdown::pdf_document2: 
    toc: false
    keep_tex: true
  bookdown::word_document2: default  
abstract: "Using annual firm survey, I follow @Dunne1988 to compute summary statistics of formal firms in Vietnam from 2000 to 2015. "
keywords: " "
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: margin=1in
fontfamily: charter
fontsize: 12pt
bibliography: "entry_exit.bib"
link-citations: true
---

```{r setup, include=FALSE}
# Chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  #warning=FALSE, 
  #message=FALSE,
  #fig.width = 6,
  fig.asp = 0.8,
  out.width = "90%"
)
```

```{r load-files, include= FALSE}
library(here)

source(file = here("inst", "rmd", "required_packages.R"))
```

```{r bibtex, include=FALSE, eval=FALSE}
file.copy(from = "/Volumes/GoogleDrive/My Drive/MendeleyBibTeX/entry_exit.bib", 
          to = here("inst", "rmd"), 
          overwrite = T)
```

```{r theme-ggplot2, echo = FALSE}
library(ggplot2)

theme_nghiem <- function(base_size = 14) {
  theme_classic(base_size = base_size) %+replace%
    theme(
      # L'ensemble de la figure
      plot.title = element_text(size = rel(1), face = "bold", margin = margin(0,0,5,0), hjust = 0),
      # Zone où se situe le graphique
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      # Les axes
      axis.title = element_text(size = rel(0.85)),
      axis.text = element_text(size = rel(0.70)),
      #axis.line = element_line(color = "black", arrow = arrow(length = unit(0.3, "lines"), type = "closed"))
      # La légende
      legend.title = element_text(size = rel(0.85), face = "bold"),
      legend.text = element_text(size = rel(0.70)),
      legend.key = element_rect(fill = "transparent", colour = NA),
      legend.key.size = unit(1.5, "lines"),
      legend.background = element_rect(fill = "transparent", colour = NA),
      legend.position = "bottom"
    )
}
# Changing the default theme
theme_set(theme_nghiem())
```

# Single plant share

```{r single-plant-g, fig.align='center', fig.cap= 'Single plant share'}
knitr::include_graphics(path = here("inst", "tmp", "figure",
                                    "single_plant_share.png"))
```

# Entry and exit of all firms

```{r entry-exit-dta, include= F}
entry_exit_dta <- fread(here("inst", "tmp", "entry_exit_dta.csv"))

Dunne98Table <- function(dta){
    
    t_dta <- dcast(melt(dta, id.vars = "svyear"), 
     variable ~ svyear, 
     value.var = "value")

    t_dta[t_dta$variable %like% "E", type := "entry"]
    t_dta[t_dta$variable %like% "X", type := "exit"]
    
    t_dta <- t_dta[order(type), !c("type")]
    
    t_dta$variable <- c("Entry Rate (ER)", 
                        "Entrant Market Share (ESH)",
                        "Entrant Relative Size (ERS)",
                        "Exit Rate (XR)",
                        "Exiter Market Share (XSH)",
                        "Exiter Relative Size (XRS)")
    
    #colnames(t_dta)[1] <- " "
    
    return(t_dta)
}

t_entry_exit <- Dunne98Table(entry_exit_dta)

```


```{r entry-exit-g, fig.align='center', fig.cap= 'Entry-Exit'}
knitr::include_graphics(path = here("inst", "tmp", "figure",
                                    "entry_exit_g.png"))
```


# Manufacturing

There are 374 4-digit VSIC 1993 manufacturing industries. 

```{r entry-exit-manu, include= F}
entry_exit_manu <- fread(here("inst", "tmp", "entry_exit_ind_dta.csv"))

ind_93_des <- read_dta(here("inst", "Stata", "VSIC1993 4-digit codes and descriptions.dta")) 

entry_exit_manu <- merge(entry_exit_manu, 
      ind_93_des, 
      by = c("vsic1993"))[, manu := fcase(vsic1993 > 1500 & vsic1993 < 4000, T, 
                                          default = F)][manu == T, !c("manu")]


mean_manu <- entry_exit_manu[, lapply(.SD, function(x) mean(x, na.rm = T)), 
                by = .(svyear), 
                .SDcols = c("ER", "ESH", "ERS", "XR", "XSH", "XRS")]


manu_tab <- Dunne98Table(mean_manu)

```

```{r manu-and-all}
manu_all_dta <- merge(t_entry_exit, 
                            manu_tab, 
                      by = c("variable"), 
                      sort = F)

```



```{r entry-exit-tab}

kbl(manu_all_dta, 
    digits = 3, 
             format = "latex",
             booktabs = TRUE, 
    col.names = c("", "00-05","05-10","10-15", 
                  "00-05","05-10","10-15"), 
             caption = "Entry and exit all and manufacturing firms", 
             table.envir = "table", 
             position = "!h") %>% 
      #kable_classic(full_width = T) %>% 
    pack_rows(index = c("Entry" = 3, "Exit" = 3)) %>% 
  add_header_above(c(" " = 1, "All" = 3, "Manufacturing" = 3)) %>% 
  kable_styling(latex_options="scale_down")


```


```{r, eval=FALSE}
med_2 <- rbindlist(list(entry_exit_dta[, manu := F], 
               mean_manu[, manu := T]), 
               use.names = T)

kbl(med_2[, .(Year = svyear, 
              ER, ESH,ERS, 
              XR, XSH, XRS)], 
    digits = 3, 
             format = "latex",
             booktabs = TRUE, 
    #col.names = c("", "2000-2005","2005-2010","2010-2015", 
    #              "2000-2005","2005-2010","2010-2015"), 
             caption = "Entry and exit all and manufacturing firms", 
             table.envir = "table", 
             position = "!h") %>% 
      #kable_classic(full_width = T) %>% 
    pack_rows(index = c("All" = 3, "Manufacturing" = 3)) %>% 
  add_header_above(c(" " = 1, "Entry" = 3, 
                     "Exit" = 3)) 
#%>% 
#  kable_styling(latex_options="scale_down")

```



## Discussion
Compare to the US 
```{r us-dta}
us_dta <-tibble( "variable"  = c("ER", "ESH", "ERS", "XR", "XSH", "XRS"), 
                 "1963-1967" = c(.307, .136, .369, .308, .144, .367), 
                 "1967-1972" = c(.427, .185, .359, .390, .191, .367), 
                 "1972-1977" = c(.408, .169, .324, .372, .173, .344))

kbl(us_dta,  
             format = "latex",
             booktabs = TRUE, 
    col.names = c("", "1963-1967","1967-1972","1972-1977"), 
             caption = "Entry and exit of US manufacturing firms", 
             table.envir = "table", 
             position = "!h") %>% 
      #kable_classic(full_width = T) %>% 
    pack_rows(index = c("Entry" = 3, "Exit" = 3))


```


1.  Entry rate is about 4 times that of the US.
2.  The other rates are comparable

Why entry rate is so high?

1.  The annualized rate seems comparable to @McCaig2021 who reports the entry rate of firms 2000-2017 at 27% annually. Thus, the data seem trustworthy.
2.  The rate is high even compared to developing countries as documented in @McCaig2021 and much higher than developed countries. @McCaig2021 observe that this number is comparable to other countries that transition out of centrally planned economies.



# References
