---
title: "Skill intensity over years"
output: bookdown::pdf_document2 
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(VNFirmSurvey)
library(data.table)
library(ggplot2)
library(DataExplorer)
library(here)
library(haven)
```

```{r}
data("skill_07_dta")
data("skill_01_dta")

dta_list <- list(skill_07_dta, skill_01_dta)

stacked_data <- rbindlist(dta_list)
```

```{r plot-skill}
stacked_data$svyear <- as.factor(stacked_data$svyear)

ggplot(stacked_data, aes(x = SI_1, col = svyear)) + 
  geom_density()

ggplot(stacked_data, aes(x = SI_2, col = svyear)) + 
  geom_density()

ggplot(stacked_data, aes(x = SI_3, col = svyear)) + 
  geom_density()
```

# Wage Data

```{r load-wage-data}

dta_list <- list(here("inst", "extdata", 
                    "Stata_2001", 
                    "dn2001.dta"), 
                 here("inst", "extdata", 
                    "Stata_2007", 
                    "dn2007.dta") )


wage_dta <- getWage(dta_list)


```

Let's take a first look at the data

```{r first-look}
plot_intro(wage_dta)

```

## Missing variables

If I use ld13 for 2001, I have more than 3000 missing observations for total labor while only 8 for ldc11.

Furthermore, 9.6% of the firms in 2001 miss total compensation data, while only 0.12% miss data

```{r missing-variable}
plot_missing(wage_dta)
profile_missing(wage_dta)
```

```{r solve-missing}
wage_dta_na_free <- na.omit(wage_dta)

wage_dta_na_free <- wage_dta_na_free[total_L > 0]
plot_missing(wage_dta_na_free)
```

## Update features

```{r features}
update_columns(wage_dta, c("tinh", "madn", "macs", "ma_thue"), as.factor)

```

## Distributions

```{r continuous}
plot_histogram(wage_dta_na_free)

summary(wage_dta_na_free)
```

## Correlation

```{r heat-map}
plot_correlation(wage_dta_na_free, maxcat = 5L)

```

## Can I link plants to firms?

```{r, eval=FALSE}
library(haven)
cn2007 <- (read_dta("/Volumes/GoogleDrive/My Drive/econ_datasets/Vietnam_VES/Data/Stata_2007_2009/Stata_2007/cn2007.dta"))  ## Maybe phieu 3.3 chi phi 

festive_exp <- (read_dta("/Volumes/GoogleDrive/My Drive/econ_datasets/Vietnam_VES/Data/Stata_2007_2009/Stata_2007/ds2007.dta", 
                         encoding="latin1"))  
names(festive_exp)


setDT(festive_exp)

festive_exp[!duplicated(macs), .(tinh, macs) ,by = .(madn)][order(madn)]

View(head(festive_exp))

```

It looks like this is a firm survey, and not a plant survey because the plants are listed under tencn, while madn and macs are firm identifiers.

find out across years what information I have at the plants level.
