---
title: "Survey details"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# FAQ

1.  What the difference between macs and madn?

# 2000

Based on Enterprise Survey Plan 2001:

> Objects of the survey are enterprises (including corporations) that are established, subject to regulation by the State Enterprise Law, Law on Cooperatives, Law on Enterprises, and Law on Foreign Investment in Vietnam, Treaties signed by the Vietnamese government with foreign governments, and the government's decrees.

The scope of the survey covers all registered business. The data are used to build the I/O table

## Plants versus enterprises

The survey distinguishes surveyed versus listed enterprises where the former is directly surveyed by the GSO and contains richer information while the latter's information comes from other databases.

To distinguish between plants and enterprises, point 3.2 explains that

> For corporations, survey shall reflect information of the entire corporation and information of economic dependent business units.

I can interpret business units here as plants and the survey asks quite limited information about the plants (labor, product, and revenue). I am not sure if enterprises which are not corporations and still have multiplants are listed with different plants.

```{r number-duplicated-macs-2001}
library(VNFirmSurvey)
data("skill_01_dta")

dim(skill_01_dta[, .N, by = (madn)][N > 1][order(-N)])
```

## **Questionnaires and reference lists**

There are 5 questionnaires and 8 reference lists. I am looking up these reference lists.

# 2002

It seems like the survey aims at plants and not enterprises. The unit of survey is clearer this year than in 2000

> In case of corporations, each independently accounted member constitute one unit of survey; therefore, headquarter and its economically dependent/dependently accounted units constitute one unit of survey.
>
> In case of parent-subsidiary companies, the parent company constitutes one unit of survey, each subsidiary company constitutes one unit of survey.

# 2003

Two types of surveys

1.  1A-DTDN applies for all domestic firms with more than 10 workers, 20% domestic firms below 10 workers, and **all** FDI
2.  1B-DTDN applies to domestic firms below 10 workers

# 2004

similar to 2004.

# 2005

Later on, it looks like the survey focuses on enterprises

## Reference lists

-   [x] List of activities of the national economy about 1000 product 6-digits (dmcn6)

-   [x] List of administrative units ( Đơn vị hành chính) (applies the 2004 Decree 124/2004/QD-TTg and new admin units till 2006). (dmhc_2005)

-   [x] Country list (dmnuoc)

-   [x] The list of products of industry, transportation, and telecommunications dm_sanPham_2005

-   [x] list of industry products featuring the newly-improved production capacity dm_CTXD_2005.

# 2006

## Reference lists

-   [x] List of activities of the national economy (5-digit code). (dmcn6)

-   [x] List of administrative units (use the list of administrative units of Vietnam in 2006 issued under Decision No. 124/2004/QD-TT dated 08/7/2004 of the Prime minister and changes updated as of June 30 2006) and the new administrative units established from July 1st to December 31st 2006.. (dmhc_2006)

-   [x] Country list (dmnuoc)

-   [x] The list of products of industry, transportation, and telecommunications dm_sanPham

-   [x] list of industry products featuring the newly-improved production capacity dm_CTXD_2005.

# 2007

## Reference lists

-   [x] ) List of activities of the national economy (5-digit code). (dmcn6)

-   [x] List of administrative units (use the list of administrative units of Vietnam in 2006 issued under Decision No. 124/2004/QD-TT dated 08/7/2004 of the Prime minister and changes updated as of June 30 2006) and the new administrative units established from July 1st to December 31st 2006.. (dmhc_2007)

-   [x] Country list (dmnuoc)

-   [x] The list of products of industry, transportation, and telecommunications dm_sanPham

-   [x] list of industry products featuring the newly-improved production capacity dm_CTXD_2005.
